Data_visualization

### 2018-06-20 Rmd/Data_visualization.Rmd
changes in ggplot

# OVULES BRASSICACEAE

p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
  labs(title="Brassicaceae",x="", y = "Ovules")+
  theme(plot.title = element_text(hjust = 0.5))

>>>>

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

# OVULES BRASSICACEAE
p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Brassicaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")

#all species
#formating d, to have just the spp of interest

p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=species)+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
